### 2024-08-17 paper.tex
m

>>>>

So, our strategy will be to find a subset of \(U_{wr}\) such that \(A_{e_{wr},b}\) has some fixed Jordan form \(\mu\), and the map \(b \mapsto P\) is algebraic.
Then we can break this subset into irreducible components by putting the Springer fiber at \(b\) in correspondence with one of the \(W_{\mu,d}\).
I think this explanation of intuition is important, so I should try to make it better.
\par So, with this as our motivation, we find a Jordan basis for the matrices \(A\) with \((A, U) \in U_{wr}\).
Actually this will be unnecessarily difficult to think about; it is easiest in the case \(r = 0\).
So, we will change basis to make \(r = 0\).
Let \(\lambda' = (\lambda_1, ..., \lambda_{w - 1}, \lambda_w - r, \lambda_{w + 1}, ..., \lambda_k)\).
Let \(X'\) be in Jordan normal form with shape \(\lambda'\).
Let \(U_{wr}' = \{(A_{X', 0, b}, U) : \forall i. A_{X', 0, b} U_{i + 1} \subseteq U_i\}\).
Let \(e_{ij}'\) be a Jordan basis for \(X'\).
Let \(f_1, ..., f_n\) be a Jordan basis for the restriction of \(A_{X, 0, b}\) to \(\mathbb{}\)...
Set \(m' := m - r\), and \(n' := n + r\).
Let \(f_1', ..., f_{n'}'\) blah.
Define the linear map \(Q_{wr} : \mathbb{C}^{m + n} \to \mathbb{C}^{m + n}\) by:
\begin{itemize}
    \item For \(i \neq w\), \(e_{ij} \mapsto e_{ij}'\)
    \item For \(j \leq \lambda_w - r\), \(e_{wj} \mapsto e_{wj}'\)
    \item If \(r \neq 0\), then \(e_{w,\lambda_w} \mapsto f_1'\), and blah.
\end{itemize}

We begin by choosing a new basis to simplify things by setting \(a = 0\) (that is, we will work with the matrices of the form \(A_{X',0,b'}\)).
Here is the new basis.
For \(i \neq w\), take the chain beginning with \(e_{i,\lambda_i}\).
Then take the chain beginning with \(e_{w,r - 1}\).
